Query Optimization for Dynamic Imputation

### 2017-05-15 paper/experiments.tex
cleaned up figure and some review paragraphs

\subsubsection{American Community Survey}
For our final experiment, we run a simple aggregate query over data from the American
Community Survey (ACS), a comprehensive survey conducted by the U.S.
Census Bureau. We use a cleaned version of the 2012 Public Use Microdata Sample (PUMS)
data kindly provided by \citeauthor*{akande2015empirical}. Given that the data had
been cleaned, we artificially dirtied it by replacing 40\% of the values uniformly at random with \nullv{} values.
The final dataset consists of 671,153 rows and 37 integer columns.

@@

We evaluate \ProjectName{} optimizing for quality ($\alpha=0$), optimizing for performance
($\alpha=1$), and targeting a balance of each ($\alpha = 0.5$). As a baseline, we fully impute the tables
used by each query and then run the query on the imputed tables, simulating the process that
an analyst would follow to apply existing imputation techniques.

@@

\review{
We also experiment with mean-value imputation and hot
deck imputation (\Cref{sec:imputation}). One approach to
mean-value imputation, to facilitate non-blocking operation within the iterator
model, is to estimate the column mean from base table histograms. In this case,
imputations are identical no matter where the operator is placed in the query
plan. Moreover, runtimes are essentially identical regardless of the value of
$\alpha$ because the time cost of the imputation is relatively low no matter
how many tuples need to be imputed. In hot deck imputation, runtimes are also
similar across $\alpha$, because the cost of buffering
tuples and sampling at random is negligible compared to the rest of query
execution. \todo{be quantitative: In terms of accuracy, relative errors using hot deck are close to
zero; since the baseline, in this case, is hot deck imputation on the base
table, only skew in the distributions arising from filters and joins would lead
to larger errors. In some cases, skew does arise, and errors are on the same
magnitude as in the decision trees case. Indeed, \ProjectName{} yields larger
benefit when using relatively sophisticated, higher quality imputation
algorithms as opposed to simpler strategies that would even be quick to
implement on the base table.
}
}

@@

\Cref{fig:pareto-frontiers} shows the final Pareto frontiers produced by the planner for \Cref{q1} and \Cref{q6}. These are the resulting set of plans after pruning dominated plans throughout our algorithm.
and encapsulate the possible trade-offs that the user can make in choosing a final plan for execution. The frontier is available at the end of the planning stage and
can be exposed to the user to help in guiding their workflow.
}

>>>>

\subsubsection{American Community Survey}
For our final experiment, we run a simple aggregate query over data from the American
Community Survey (ACS), a comprehensive survey conducted by the U.S.
Census Bureau. We use a cleaned version of the 2012 Public Use Microdata Sample (PUMS). Given that the data had
been cleaned, we artificially dirtied it by replacing 40\% of the values uniformly at random with \nullv{} values.
The final dataset consists of 671,153 rows and 37 integer columns.

@@

\review{We evaluate \ProjectName{} optimizing for quality ($\alpha=0$), optimizing for performance
($\alpha=1$), and targeting a balance of each ($\alpha = 0.5$). As a baseline, we fully impute the tables
used by each query and then run the query on the imputed tables, simulating the process that
an analyst would follow to apply existing imputation techniques.}

@@

\review{
We also experiment with mean-value imputation and hot
deck imputation (\Cref{sec:imputation}). One approach to
mean-value imputation, to facilitate non-blocking operation within the iterator
model, is to estimate the column mean from base table histograms. In this case,
imputations are identical regardless of where the operator is placed in the query
plan. Moreover, runtimes are essentially identical regardless of the value of
$\alpha$ because the time cost of the imputation is relatively low independent of
how many tuples need to be imputed. In hot deck imputation, runtimes are also
similar across $\alpha$, because the cost of buffering
tuples and sampling at random is negligible compared to the rest of query
execution. \todo{be quantitative: In terms of accuracy, relative errors using hot deck are close to
zero; since the baseline, in this case, is hot deck imputation on the base
table, only skew in the distributions arising from filters and joins would lead
to larger errors. In some cases, skew does arise, and errors are on the same
magnitude as in the decision trees case. Indeed, \ProjectName{} yields larger
benefit when using relatively sophisticated, higher quality imputation
algorithms as opposed to simpler strategies that would even be quick to
implement on the base table.
}
}

@@

\Cref{fig:pareto-frontiers} shows the final Pareto frontiers produced by the planner for \Cref{q1} and \Cref{q6}. These are the resulting set of plans after pruning dominated plans throughout our algorithm.
and encapsulate the possible trade-offs that the user can make in choosing a final plan for execution. The frontier is available at the end of the planning stage and
can be exposed to the user to guide their workflow.
}
